\documentclass[a4paper,10pt]{article}

\usepackage{parskip} 
\usepackage{hologo}
\usepackage{fontspec}

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.42\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright\color[HTML]{000435}}{}{0em}{}[\titlerule]
\titlespacing{\section}{1pt}{2pt}{2pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\color[HTML]{110223}%{1C033C}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
% \usepackage{times}

% For underline
\usepackage[normalem]{ulem}

\setmainfont{Calibri}  % Set it to whatever you like

\begin{document}

% non-numbered pages
\pagestyle{empty} 


\begin{tabularx}{\linewidth}{@{} C @{}}
\color[HTML]{000435} \Huge{Mohd Hassan Khan} \\[6pt]
\\
\textcolor[HTML]{000435}{\faPhone} +91-9137985667 | Mumbai, Maharashtra, INDIA \\
\textcolor[HTML]{000435}{\faEnvelope} \underline{\href{mailto:hassankhan2608@gmail.com}{hassankhan2608@gmail.com}} | 
\textcolor[HTML]{000435}{\faLinkedin} \underline{\href{https://www.linkedin.com/in/hassankhan2608/}{linkedin.com/in/hassankhan2608/}} | 
\textcolor[HTML]{000435}{\faGlobe} \underline{\href{https://hassankhan2608.github.io/}{hassankhan2608.github.io}}
\end{tabularx}

\section{Summary}
Insightful and results-driven data analyst with expertise in converting raw data into meaningful insights through data analytics, machine learning, and statistical modeling. Skilled in leveraging Python, SQL, and data visualization tools to uncover actionable insights and drive data-informed decisions. A quick learner with a passion for solving complex problems through data-driven solutions.

\section{Education}
\textbf {Rizvi College of Arts, Science and Commerce} & \hfill 2020-2023 \\
Bachelor of Science in Information Technology & \hfill CGPA : 7.67\\

\section{Courses and Certifications}
\begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
    \item Data Science \& Business Analytics - Boston Institute of Analytics [Offline Training] 
    \item Data Analysis and Visualization with Python - IBM \& Coursera
    \item Databases and SQL for Data Science with Python - IBM \& Coursera \\
\end{itemize}

% Skills
\section{Skills}
\begin{multicols}{4}
\begin{itemize}
    \item Python
    \item SQL
    \item Excel
    \item Google Sheets
    \item PowerPoint
    \item Tableau
    \item Power BI
    \item ETL
    \item EDA
    \item Statistical Analysis
    \item Data Visualization
    \item Data Cleaning
    \item Machine Learning
    \item NLP
    \item Pandas, Numpy
    \item Seaborn, Matplotlib
\end{itemize}
\end{multicols}


\section{Professional Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf {Data Science Intern, iNeuron.AI} \hfill Dec 2023 - Mar 2024 \\[4pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Converted raw data into meaningful insights, enabling data-driven decision-making across the organization.
        \item Developed and optimized data cleaning processes, reducing data errors by 20\% and improving overall data quality.
        \item Automated data extraction and transformation processes using Python, decreasing preprocessing time by 30\% and enabling more in-depth analysis.
    \end{itemize}
\end{minipage}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf {Data Analyst Intern, Meri Skill} \hfill Nov 2023 - Dec 2023 \\[4pt]
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=2em, itemsep=2pt]
        \item Transformed complex data sets into actionable visualizations, enabling stakeholders to make informed decisions.
        \item Analyzed sales data to identify trends, patterns, and insights for strategic planning and decision-making.
        \item Provided HR analytics insights for workforce optimization, supporting data-driven decision-making in talent management.
    \end{itemize}
\end{minipage}
\end{tabularx}

\section{Projects}
\begin{enumerate}[label={}, nosep, after=\strut, leftmargin=2em, itemsep=2pt]
    \item \textbf {Bank Marketing Analysis with Power-BI Dashboard \& Forecasting Model} \hfill 
    [\underline{\href{https://portuguese-bank-marketing-analysis.onrender.com}{Live}}]~[\underline{\href{https://www.linkedin.com/posts/hassankhan2608_datascience-capstoneproject-powerbi-activity-7138464571496869888-NegR?utm_source=share&utm_medium=member_desktop}{Video}}]~[\underline{\href{https://github.com/hassankhan2608/-PORTUGUESE-BANK-MARKETING-ANALYSIS}{Github}}]
        \begin{itemize}[nosep, after=\strut, itemsep=2pt]
            \item Extracted valuable insights from marketing data, enabling data-driven campaign strategies.
            \item Performed comprehensive data wrangling, interpretation, and visualization using Python libraries.
            \item Developed predictive models for forecasting marketing campaign success.
            \item Created interactive Power BI dashboards, increasing data accessibility and comprehension by 15\%.
        \end{itemize}
    \item \textbf {Bank Customer Churn Analysis with Power-BI Dashboard \& Forecasting Model} \hfill 
    [\underline{\href{https://bank-customer-churn-analysis-stmz.onrender.com}{Live}}]~[\underline{\href{https://www.linkedin.com/posts/hassankhan2608_datascience-capstoneproject-powerbi-activity-7138464571496869888-NegR?utm_source=share&utm_medium=member_desktop}{Video}}]~[\underline{\href{https://github.com/hassankhan2608/Bank-Customer-Churn-Analysis}{Github}}]
        \begin{itemize}[nosep, after=\strut, itemsep=2pt]
            \item Identified key drivers of customer churn, informing targeted retention initiatives.
            \item Developed classification models for predicting customer churn, enabling proactive retention strategies.
            \item Designed dynamic Power BI dashboards for data visualization and stakeholder communication.
        \end{itemize}
    \item \textbf {Reviews Sentiments Analysis \& Prediction} \hfill [\underline{\href{https://www.linkedin.com/posts/hassankhan2608_datascience-nlp-sentimentanalysis-activity-7139969581443436544-DGh4?utm_source=share&utm_medium=member_desktop}{Video}}]~[\underline{\href{https://github.com/hassankhan2608/Sentiment-Analysis-on-Amazon-Alexa-Review}{Github}}]
        \begin{itemize}[nosep, after=\strut, itemsep=2pt]
            \item Leveraged sentiment analysis to uncover customer pain points and preferences, guiding product development.
            \item Employed natural language processing techniques for sentiment analysis of customer reviews.
        \end{itemize}
    \item \textbf {Resume-Guru Gen-AI (Google Gemini LLM)} \hfill
    [\underline{\href{https://resume-guru-wekk.onrender.com}{Live}}]~[\underline{\href{https://www.linkedin.com/posts/hassankhan2608_resumeguru-jobsearch-ai-activity-7168492456827723776-WYjC?utm_source=share&utm_medium=member_desktop}{Video}}]~[\underline{\href{https://github.com/hassankhan2608/Resume-Guru}{Github}}]
        \begin{itemize}[nosep, after=\strut, itemsep=2pt]
            \item Developed an AI-powered web application for resume optimization and job matching.
            \item Built an intuitive web interface using Python and Streamlit for user-friendly interaction.
        \end{itemize}
\end{enumerate}

\end{document}